Are We Reusing Outdated Code from Stack Overflow?

### 2017-01-23 cloneoverflow-latex/cloneoverflow.tex
Updated throughout the paper

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,448 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.

@@

\vspace{0.5ex}%
\noindent\textbf{3.~Online code clone oracle:} The 3,448 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.

@@

\subsection{Clone Detector's Parameter Tuning}
We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors with two chosen configurations each, we look for Bellon's good and ok-match in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
	\resizebox{\columnwidth}{!}{%
		\scriptsize
\begin{tabular}{l|p{5.5cm}}
	\hline 
	Tool & Parameters \\
	\hline
	Simian$_{\textrm{\textit{df}}}$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
	\hline
	Simian$_{\textrm{\textit{EvCl}}}$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
	\hline 
	NiCad$_{\textrm{\textit{df}}}$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
	\hline
	NiCad$_{\textrm{\textit{EvCl}}}$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
	\hline 
\end{tabular} %
}
\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\
			\hline
			Snippets & 1,086 & 1,530 & 1,240 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,372,599 & 229,176 & 206,760,077 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,447 & 185 & 16,047 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.64 & 5.32 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement}
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r}
		\hline
		Setting & No.~of clone pairs \\ 
		\hline 
		%\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  \\
		%\multirow{1}{*}{\textit{ok-match(0.7)}}    & 29,099 \\
		\multirow{1}{*}{\textit{agreed clone pairs}}        & 31,360 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}}       & 871    \\
		%\multirow{1}{*}{\textit{NiCad$_{df}$}}        & 168    \\ 
		\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total                                               & 32,399 \\ 
		\hline
	\end{tabular} 
\end{table}

The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by Simain$_{df}$ and 1,530 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones in 1,240 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.72 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.79. Similarly, NiCad$_{df}$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 29\%, 28\%, 25\%, and 21\% accordingly.

As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match and ok-match between combination of Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is reduced to 31,360. The number of disagreed clone pairs after filtering is 1,039. The details are as follows.

\begin{table}
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.  Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We found that NiCad generates errors and stopped processing against some Qualitas projects. \FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ could not detect clones in 6 projects due to clustering errors. NiCad$_{\textrm{\textit{EvCl}}}$ generated renaming errors for 11 projects, and clustering errors for 16 projects. Hence, we did not have NiCad clones in the agreed clone pairs for these 6 (NiCad$_{\textrm{\textit{df}}}$) and 27 projects (NiCad$_{\textrm{\textit{EvCl}}}$). This makes Simian clones of the same projects to be removed from the agreed clone pairs as well since they could not have matching online clone pairs.

The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}. There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. According to the definition, ok-match clone pairs always subsume the good-match pairs. As a result, there are 29,944 ok-match clone pairs. 9,062 pairs are from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs are from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 are pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs are from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{3}{c}{No.~of clone pairs}   \\
		\hline
		Simian          & NiCad             & good-match & ok-match & Total  \\
		\hline
		\textit{df}     & \textit{df}       & 10 	     & 9,062    & 9,072  \\ 
		\textit{df}     & \textit{EvCl}     & 26 	     & 1017     & 1,043  \\ 
		\textit{EvCl} 	& \textit{df} 	    & 10 	     & 88       & 98     \\
		\textit{EvCl} 	& \textit{EvCl}     & 2,228      & 19,777   & 22,005 \\ 
		\hline
		\multicolumn{2}{l|}{Total}          & 2,274      & 29,944   & 32,218 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2,261      & 29,099   & 31,360 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{venn4_pairs_good_pt1+2}
		\caption{Distributions of good-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2+3}
		\caption{Distributions of ok-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with another tool. The disagreement can be from misalignment of clone lines or different configurations that result in different clones reported. They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs. With the four configuration combinations, we decided to investigate only two, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively). They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.

@@

% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
For Simian$_{df}$, there are 20,348 clone pairs after using 10--line filter. Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded. We filtered the results further by removing false positives such as similar \verb|equals()|, \verb|hashCode()| methods, getters and setters out by using regular expressions. We managed to reduce the number to 871 clone pairs remaining for manual investigation. 
% 7062 + 22187 + 6755 =  36004 %
For NiCad$_{df}$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. We thus filter NiCad's clones by using similarity threshold. We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2) and obtain 618 clone pairs. %However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. So . Using 80\% similarity, there are totally 166 pairs left. 
There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation. The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.

@@

\begin{table}
	\centering
	\caption{Statistics of disagreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline \& reg.~expressions & \multirow{2}{*}{67,570} & \multirow{2}{*}{2,546} & \multirow{2}{*}{871} \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ \newline (i.e.~UPI=0.2) & \multirow{2}{*}{229,176} & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
		\hline
		\multicolumn{2}{l|}{Total} & 296,746 & 2,996 & 1,039 \\
		\hline
	\end{tabular} %
	}
\end{table}

\subsection{RQ2: Reasons for Creating Online Code Clones}

\begin{table}
	\centering
	\caption{Seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{|c|p{8cm}|}
			\hline 
			Cat. & Descriptions \\ 
			\hline 
			A & Cloned from Qualitas to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			A' &Cloned from Stack Overflow to Qualitas (S $\rightarrow$ Q). \\ 
			\hline 
			B & Cloned from each other or from an external source \textit{X} (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			C & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			D & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			E & Inheritance, interface implementation 
			\\ 
			\hline 
			F & Accidental similarity, false clones by normalisation \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

>>>>

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,450 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.

@@

\vspace{0.5ex}%
\noindent\textbf{3.~Online code clone oracle:} The 3,450 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.

@@

\subsection{Clone Detector's Parameter Tuning}
We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we look for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
	\resizebox{\columnwidth}{!}{%
		\scriptsize
\begin{tabular}{l|p{5.5cm}}
	\hline 
	Tool & Parameters \\
	\hline
	Simian$_{\textrm{\textit{df}}}$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
	\hline
	$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
	\hline 
	$N_D$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
	\hline
	$N_E$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
	\hline 
\end{tabular} %
}
\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,530 & 1,240 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,372,599 & 229,176 & 206,760,077 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,447 & 185 & 16,047 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.64 & 5.32 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement and \texttt{equals()}}
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r|r|r}
		\hline
		Clone set & C$_{\textrm{\textit{pairs}}}$ & \texttt{equals()} & Manual \\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  & 9 & 2,252 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 26,838 & 9,122 & 200 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
		\multirow{1}{*}{$S_D$}       & 17,801 & 16,930 & 871 \\
		\multirow{1}{*}{$N_D$}       & 168 & 41 & 127 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total                                               & 47,068 & 26,102 & 3,450 \\ 
		\hline
	\end{tabular} 
\end{table}

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,530 from $S_E$ respectively. $N_D$ reports clones in 1,240 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}. The average clone size of$S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to$S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.

As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match is reduced to 2,261 while ok-match is reduced to 26,838. The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 168 for Simian and NiCad respectively. The details are as follows.

\begin{table}
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
		\textit{Clustering fail} & -- & -- & 6 & 16 \\
		\textit{Renaming fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.  Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We found that NiCad generates errors and stopped processing against some Qualitas projects. \FIXME{Report the errors to NiCad creator.}  $N_D$ could not detect clones in 6 projects due to clustering errors. $N_E$ generated renaming errors for 11 projects, and clustering errors for 16 projects. Hence, we did not have NiCad clones in the agreed clone pairs for these 6 ($N_D$) and 27 projects ($N_E$). This makes Simian clones of the same projects to be removed from the agreed clone pairs as well since they could not have matching online clone pairs.

The distributions of good-match clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}. There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from$S_DN_D$, 26 pairs from$S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$. According to the definition, ok-match clone pairs always subsume the good-match pairs. There are 26,838 ok-match clone pairs (excluding the 2,261 good-match pairs). 9,052 pairs are from $S_DN_D$, 991 pairs are from $S_DN_E$, 78 are pairs from $S_EN_D$, and 17,549 pairs are from $S_EN_E$. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations. If we remove duplicates, the number of unique ok-match pairs is 26,838.

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{D} and \textit{E} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|r|r}
		\hline
		\multirow{2}{*}{Setting} & \multicolumn{2}{c}{No.~of clone pairs}   \\ \cline{2-3}
		& good-match & ok-match \\
		\hline
		$S_DN_D$  & 10 & 9,052    \\ 
		$S_DN_E$  & 26 & 991     \\ 
		$S_EN_D$  & 10 & 78       \\
		$S_EN_E$  & 2,228 & 17,549   \\ 
		\hline
		Total & 2,274 & 27,670   \\
		\hline
		Unique & 2,261 & 26,838  \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3}
		\caption{Distributions of good-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3}
		\caption{Distributions of ok-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with another tool. The disagreement can be from misalignment of clone lines or different configurations that result in different clones reported. They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs. With the four configuration combinations, we decided to investigate only two,$S_D$, and $N_D$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively). They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.

@@

% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
For $S_D$, there are 20,348 clone pairs after using 10--line filter. Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded. We filtered the results further by removing false positives such as similar \verb|hashCode()| methods, getters and setters out by using regular expressions. We managed to reduce the number to 871 clone pairs remaining for manual investigation. 
% 7062 + 22187 + 6755 =  36004 %
For $N_D$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. We thus filter NiCad's clones by using similarity threshold. We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2) and obtain 618 clone pairs. %However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. So . Using 80\% similarity, there are totally 166 pairs left. 
There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation. The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.

@@

\begin{table}
	\centering
	\caption{No.~of disagreed clone pairs ($S_D$ and $N_D$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{1.5cm}|r|r|r|r}
		\hline 
		Tool & Filter & \multicolumn{1}{c|}{Original} & \multicolumn{1}{c|}{Filtered} & \multicolumn{1}{c|}{good/ok} & \multicolumn{1}{c}{remaining} \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $line \geq 10$ \newline \& reg.~exp & \multirow{2}{*}{67,570} & \multirow{2}{*}{47,223}  & \multirow{2}{*}{2,546} & \multirow{2}{*}{17,801} \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{$N_D$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{$N_D$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{$N_D$}} & $sim \geq 80\%$ \newline (UPI=0.2) & \multirow{2}{*}{229,176} & \multirow{2}{*}{228,558}  & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
		\hline
		%\multicolumn{2}{l|}{Total} & 296,746 & 20,966 & 2,996 & 1,039 \\
		%\hline
	\end{tabular} %
	}
\end{table}

\subsection{RQ2: Patterns of Online Code Cloning}

\begin{table}
	\centering
	\caption{Seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{|c|p{8.4cm}|}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			A & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			A' &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			B & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			C & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			D & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			E & Inheritance, interface implementation 
			\\ 
			\hline 
			F & Accidental similarity, false clones by normalisation \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

This is an important question underpinning the motivation of online code cloning. Why are they created and how? Due to an absence of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives. At the same time, we select a reason that stimulates a creation of each online clone pair. %We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.

We started by studying the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}. We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments. This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study. Using$S_D$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size. We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps). The 34 selected snippets generate 697 clone pairs. Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating. Clearly \textbf{Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}

We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new patterns observed as common cloning patterns from our preliminary investigation. The seven patterns ranging from A--F as presented in \Cref{tab:classification_scheme}. Pattern A is a cloning that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern A' is the opposite of A. Pattern B is a cloning that is exactly identical or highly similar but without any attribution of copying. Pattern C is a cloning that has an evidence of copying from the same external source. Pattern D is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation). Pattern E is inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, F, is a false clone pair. They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process. Using this cloning pattern classification scheme, we consider clone pairs in created by pattern A, A', B, C as true positive, and clone pairs in pattern D, E, F as false positive.

\subsubsection{Manual Investigation of Clone Candidates}

The first author who has been working on clone detection research for two years takes the role of a main investigator performing manual investigation of all 3,450 clone pairs. The third author takes the role of a second investigator performing 10\% validation of the clone pairs judged by the main investigator. Following the cloning patterns, the main investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate cloning pattern for the pair. A relevant and useful observation is also recorded for each clone pair.
